Assessing glymphatic transport velocities by adjoint methods

### 2018-10-02 tex/paper.tex
Bilder

Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
However, in \cite{xie2013sleep} a 60% coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.

@@

An outline of the paper is as follows. In Section 2 we descibe the medical images and their modality,  
and the mathematical methodology used for determining the apparent diffusion coefficients.

@@

The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
\begin{equation}
u        d U_prev + \Delta t - dt U.
\end{equation}
Here $dt$ is forward timestep and $\Delta t$ is the difference between ?? 
The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

@@

\begin{figure}
\includegraphics[width=0.95\textwidth]{GMRI.png} 
\label{fig1} 
\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
\end{figure}

\comment{Lars: bilde av konkret mesh  }

\begin{figure}
\includegraphics[width=0.3\textwidth]{mesh-eps-converted-to.pdf} 
\label{fig1} 
\caption{\comment{lars, we will need some new images since I believe this is stolen from JCI}}
\end{figure}

@@

\begin{table}
\centering
\caption{ tau = double  }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
\hline
 1.0e-05 	 & 1.0e-02 	 & 20 & 429 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 386 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
\end{tabular}}
\label{Tab::2}
\end{table}

\begin{table}
\centering
\caption{ tau = double  }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & wrong$g$ \\
\hline
 1.0e-05 	 & 1.0e-03 	 & 40 & 210 	 & +0.019 & +0.005 & -0.001 & +0.002 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 597 	 & +0.006 & +0.015 & -0.008 & +0.017 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 910 	 & +0.046 & +0.047 & -0.020 & +0.065 \\ 
\end{tabular}}
\label{Tab::2}
\end{table}

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.015 amp }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline

\end{tabular}}
\label{Tab::3}
\end{table}

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.03 amp }
\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline
 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\

@@

\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. Noise 0.3 amp }

@@

%\begin{table}
%\centering
%\caption{ $\tau = [1.0, 1.2, 1.4, 2.8, 4.6, 9.6, 14.4, 18.6, 22.2, 24.0] $}
%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
%\hline
%
%\label{Tab::1}
%\end{table} 
%\section{Discussion}
%
%
%\begin{table}
%\centering
%\caption{ $\tau =[1.2, 1.4, 1.8, 2.4, 3.6, 5.4, 7.6, 17.2, 18.6, 20.4, 22.4, 24.0] $}
%\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
%$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
%\hline
%
%\end{tabular}}
%\label{Tab::1}
%\end{table} 

 \begin{table}
\centering
\caption{ $\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $}
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
\hline
 1.0e-04 	 & 1.0e-02 	 & 40 & 283 	 & -0.059 & -0.020 & -0.027 & +0.331 \\ 
 \rowcolor{red} 1.0e-04 	 & 1.0e-03 	 & 40 & 247 	 & -0.062 & -0.023 & -0.030 & +0.407 \\ 
 1.0e-05 	 & 1.0e-02 	 & 40 & 400 	 & -0.059 & -0.020 & -0.027 & +0.260 \\ 
\rowcolor{red}  1.0e-05 	 & 1.0e-03 	 & 40 & 183 	 & -0.063 & -0.023 & -0.029 & +0.404 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 618 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
 1.0e-06 	 & 1.0e-01 	 & 40 & 826 	 & -0.046 & -0.013 & -0.024 & +0.070 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 632 	 & -0.058 & -0.020 & -0.027 & +0.183 \\ 
\rowcolor{red}  1.0e-06 	 & 1.0e-03 	 & 40 & 234 	 & -0.062 & -0.023 & -0.030 & +0.398 \\ 
\end{tabular}}
\label{Tab::Incoherence}
\end{table} 
\section{Discussion}

>>>>

Transportation by diffusion is in the order of XXX\comment{Lars: hente fra R. Thorne / Nicholson}. 
However, in \cite{xie2013sleep} a $60\%$ coverage of 3kDa Texas Red Dextran of a $200 \mu m$ cube was demostrated in approximately 
20 minutes. As such, the transportation is XXX faster than what diffusion would provide. Furthermore, 
in \cite{eidevalnes} it was demonstrated that X Da Gadovist was brainwide in 8 hours after injection in the lumbar region.

@@

An outline of the paper is as follows. In Section 2 we describe the medical images and their modality,  
and the mathematical methodology used for determining the apparent diffusion coefficients.

@@

The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
\begin{equation}
u_{linear} = \frac{\Delta t}{dt} U_prev + \frac{dt - \Delta t }{dt} U.
\end{equation}
Here $dt$ is forward timestep and $\Delta t$ is the difference between observation time and forward time. 
The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

@@

\begin{figure}
\includegraphics[width=0.95\textwidth]{PatID-68-new-100.png} 
\label{fig1} 
\caption{Shows the percentage intensity increase from baseline at different observation times. }
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
\label{fig1} 
\caption{Shows the percentage intensity increase from baseline at different observation times in the area corresponding to the generated mesh that is marked red in the left panel.}
\end{figure}

\begin{figure}
\includegraphics[width=0.3\textwidth]{mesh-eps-converted-to.pdf} 
\label{fig1} 
\caption{Shows the mesh created from the baseline MR image with 3 domains. ( wrap ?? ) }
\end{figure}

@@

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.03, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline
 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\

@@

\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.3, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$  }

@@

\begin{table}
\centering
\caption{ $\tau = [4.8, 9.6, 14.4, 19.2, 24.0]$}
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 1.0e-04 	 & 1.0e+00 	 & 10 & 161 	 & +0.081 & +0.027 & +0.049 & +0.023 \\ 
 1.0e-04 	 & 1.0e-01 	 & 10 & 185 	 & +0.123 & +0.046 & +0.037 & +0.021 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 265 	 & +0.160 & +0.082 & +0.033 & +0.016 \\ 
 1.0e-05 	 & 1.0e+00 	 & 10 & 192 	 & +0.083 & +0.026 & +0.049 & +0.023 \\ 
 1.0e-05 	 & 1.0e-01 	 & 10 & 223 	 & +0.118 & +0.047 & +0.037 & +0.020 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 267 	 & +0.159 & +0.084 & +0.033 & +0.016 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 176 	 & +0.082 & +0.026 & +0.049 & +0.023 \\ 
 1.0e-06 	 & 1.0e-01 	 & 10 & 229 	 & +0.120 & +0.046 & +0.037 & +0.021 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 253 	 & +0.156 & +0.080 & +0.033 & +0.018 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 202 	 & +0.007 & -0.050 & +0.017 & +0.028 \\ 
 1.0e-04 	 & 1.0e-01 	 & 20 & 336 	 & +0.028 & -0.009 & +0.009 & +0.023 \\
 1.0e-04 	 & 1.0e-02 	 & 20 & 320 	 & +0.025 & +0.025 & +0.015 & +0.013 \\ 
 1.0e-05 	 & 1.0e+00 	 & 20 & 195 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
 1.0e-05 	 & 1.0e-01 	 & 20 & 320 	 & +0.029 & -0.011 & +0.009 & +0.026 \\ 
 1.0e-05 	 & 1.0e-02 	 & 20 & 351 	 & +0.023 & +0.017 & +0.011 & +0.019 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 224 	 & +0.007 & -0.051 & +0.017 & +0.029 \\ 
 1.0e-06 	 & 1.0e-01 	 & 20 & 334 	 & +0.027 & -0.012 & +0.009 & +0.026 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 340 	 & +0.020 & +0.016 & +0.012 & +0.019 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 308 	 & -0.032 & -0.081 & +0.002 & +0.031 \\ 
 1.0e-04 	 & 1.0e-01 	 & 40 & 379 	 & -0.004 & -0.033 & -0.006 & +0.026 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 377 	 & +0.006 & +0.006 & -0.001 & +0.008 \\ 
 1.0e-05 	 & 1.0e+00 	 & 40 & 212 	 & -0.034 & -0.083 & +0.001 & +0.031 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 396 	 & -0.007 & -0.036 & -0.006 & +0.028 \\ 
 1.0e-05 	 & 1.0e-02 	 & 40 & 374 	 & +0.009 & +0.007 & -0.003 & +0.014 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 226 	 & -0.034 & -0.082 & +0.001 & +0.031 \\ 
 1.0e-06 	 & 1.0e-01 	 & 40 & 313 	 & -0.007 & -0.037 & -0.006 & +0.030 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 368 	 & +0.006 & +0.006 & -0.004 & +0.013 \\ 
\end{tabular}}
\end{table}

\begin{table}
\centering
\caption{ Shows the $\tau = [1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] $}
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 1.0e-04 	 & 1.0e+00 	 & 10 & 246 	 & -0.046 & +0.038 & +0.023 & +0.031 \\ 
 1.0e-04 	 & 1.0e-01 	 & 10 & 292 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 338 	 & -0.053 & +0.038 & +0.024 & +0.032 \\ 
 1.0e-05 	 & 1.0e+00 	 & 10 & 290 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
 1.0e-05 	 & 1.0e-01 	 & 10 & 316 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 389 	 & -0.052 & +0.038 & +0.024 & +0.033 \\ 
 1.0e-06 	 & 1.0e+00 	 & 10 & 282 	 & -0.047 & +0.038 & +0.023 & +0.031 \\ 
 1.0e-06 	 & 1.0e-01 	 & 10 & 308 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 285 	 & -0.052 & +0.038 & +0.024 & +0.032 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 228 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
 1.0e-04 	 & 1.0e-01 	 & 20 & 331 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
 1.0e-04 	 & 1.0e-02 	 & 20 & 367 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
 1.0e-05 	 & 1.0e+00 	 & 20 & 194 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
 1.0e-05 	 & 1.0e-01 	 & 20 & 312 	 & -0.001 & +0.018 & +0.006 & +0.006 \\ 
 1.0e-05 	 & 1.0e-02 	 & 20 & 266 	 & +0.004 & +0.018 & +0.005 & +0.007 \\ 
 1.0e-06 	 & 1.0e+00 	 & 20 & 179 	 & -0.008 & +0.016 & +0.009 & +0.006 \\ 
 1.0e-06 	 & 1.0e-01 	 & 20 & 245 	 & -0.002 & +0.018 & +0.006 & +0.006 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 362 	 & +0.003 & +0.018 & +0.005 & +0.007 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 279 	 & -0.007 & +0.000 & +0.003 & +0.002 \\ 
 1.0e-04 	 & 1.0e-01 	 & 40 & 313 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 273 	 & +0.017 & +0.006 & -0.001 & +0.001 \\ 
 1.0e-05 	 & 1.0e+00 	 & 40 & 238 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 317 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
 1.0e-05 	 & 1.0e-02 	 & 40 & 336 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 261 	 & -0.007 & +0.000 & +0.002 & +0.002 \\ 
 1.0e-06 	 & 1.0e-01 	 & 40 & 318 	 & +0.004 & +0.003 & +0.000 & +0.002 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 375 	 & +0.015 & +0.005 & -0.001 & +0.001 \\ 
\end{tabular}}
\end{table}

\begin{table}
\centering
\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.0}
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
 1.0e-04 	 & 1.0e+00 	 & 40 & 517 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
 1.0e-04 	 & 1.0e-01 	 & 40 & 660 	 & -0.045 & -0.013 & -0.024 & +0.052 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 283 	 & -0.059 & -0.020 & -0.027 & +0.331 \\ 
 1.0e-05 	 & 1.0e+00 	 & 40 & 588 	 & -0.034 & -0.006 & -0.022 & +0.060 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 686 	 & -0.046 & -0.013 & -0.024 & +0.067 \\ 
 1.0e-05 	 & 1.0e-02 	 & 40 & 400 	 & -0.059 & -0.020 & -0.027 & +0.260 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 618 	 & -0.034 & -0.006 & -0.022 & +0.058 \\ 
 1.0e-06 	 & 1.0e-01 	 & 40 & 826 	 & -0.046 & -0.013 & -0.024 & +0.070 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 632 	 & -0.058 & -0.020 & -0.027 & +0.183 \\

\end{tabular}}
\label{Tab::1}
\end{table} 
\begin{table}
\centering
\caption{$\tau = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0] $ noise 0.3}
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 1.0e-04 	 & 1.0e+00 	 & 40 & 519 	 & +0.003 & +0.029 & +0.035 & +0.067 \\ 
 1.0e-04 	 & 1.0e-01 	 & 40 & 653 	 & -0.096 & +0.015 & +0.016 & +0.070 \\ 
\rowcolor{red}  1.0e-04 	 & 1.0e-02 	 & 40 & 575 	 & -0.050 & -0.001 & +0.057 & +0.281 \\ 
 1.0e-05 	 & 1.0e+00 	 & 40 & 585 	 & -0.050 & -0.007 & +0.017 & +0.068 \\ 
 1.0e-05 	 & 1.0e-01 	 & 40 & 871 	 & -0.023 & +0.024 & +0.019 & +0.079 \\ 
\rowcolor{red}  1.0e-05 	 & 1.0e-02 	 & 40 & 466 	 & -0.045 & +0.042 & +0.019 & +0.281 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 584 	 & -0.045 & +0.019 & +0.006 & +0.071 \\ 
 1.0e-06 	 & 1.0e-01 	 & 40 & 546 	 & +0.005 & +0.019 & -0.001 & +0.079 \\ 
\rowcolor{red}  1.0e-06 	 & 1.0e-02 	 & 40 & 648 	 & -0.074 & -0.008 & +0.041 & +0.227 \\ 
\end{tabular}}
\label{Tab::1}
\end{table}
